---
title: "Downsampling"
author: "David Rach"

format: html
---

# Background

Due to trying to keep the overall file size down, I am downsampling to 100 events. For anyone interested in how I did this, this Quarto Markdown Document contains the code needed to repeat the process. 

# Getting Started

Attach the required packages via the `library()` function

```{r}
#| eval: FALSE
library(purrr) # CRAN
library(flowWorkspace) # Bioconductor
library(Luciernaga) #DavidRach/Luciernaga
```

## Specify file.path and identify files

Due to the counts being conducter on two separate instruments, the number of columns differs, so they will need to be loaded into separate GatingSet objects. 

```{r}
#| eval: FALSE
StorageLocation <- file.path("/media", "david", "DavidSSD",  "AlphaBeta", "Tcells")
Existing <- list.files(StorageLocation, pattern=".fcs", full.names=TRUE)
List1 <- Existing[c(1,3:4,6,12, 14)]
```

## Load .fcs files into a GatingSet

Load in files to their respective GatingSet objects

```{r}
#| eval: FALSE
cs1 <- load_cytoset_from_fcs(List1, truncate_max_range = FALSE, transformation = FALSE)
gs1 <- GatingSet(cs1)
```

# Downsample each sample and pass back to the folder

From here, each file in the Gating set is passed to `Utility_Downsample()`, subsampling for 100 events. In this case, subsets argument is set to "root", so all events. If we had implemented gates, we could have selected a particular population from which to downsample. 

```{r}
#| eval: FALSE
NewStorageLocation <- file.path("course", "05_GatingSets", "data")

walk(.x=gs1, .f=Luciernaga::Utility_Downsample,
 sample.name=c("$PROJ", "GROUPNAME", "TUBENAME"),
 export=TRUE, outpath=NewStorageLocation,
  subsample=10000, subsets="root", inverse.transform=FALSE)
```

# Conclusion

We will look more at how the Utility_Downsample is constructed during [Week #10](/Schedule.qmd#downsampling-and-concatenation)

```{r}
#| eval: FALSE
sessionInfo()
```